---
title: "Lab_01"
author: "Peilu Huang"
date: "2025-09-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### TODO 1: Using Markdown for Your Resume/CV
#### Peilu Huang
###### Education
* University of Washington,  *Seattle, US*  
Master of Science in Real Estate  **Sep 2024-Est. Jun 2026**  
* University of Nottingham Ningbo China,  *Ningbo, China*  
BSc (Hons) Finance, Accounting and Management  **Sep 2020-Jul 2024**

## TODO 2: R Basic Review Tasks
The simplest argument of as.Date(): an object to be converted
```{r echo=FALSE}
birthday <- as.Date("2001-09-10")
print(birthday)
class(birthday)
```
Argument of Sys.Date(): Not required
```{r echo=FALSE}
today <- Sys.Date()
print(today)
dates <- c(birthday,today)
dates[2]-birthday
8792/365
```

Today is  `r (print(today))` it has been `r ((dates[2]-birthday)/365)` years since my birthday.

## TODO 3: Explore Census Demographic Data
#### King County Household Income
```{r echo=FALSE}
library(tidycensus) 
library(tidyverse)
census_api_key("96f943fd5b38142362574386830d3c855e82dd28")
king_income <- get_acs(geography = "tract", 
            table = "B19001", 
            state = "53", 
            county = "033", 
            year = 2023)
```

mean `r ( mean(king_income$estimate, na.rm = TRUE))`
median `r ( median(king_income$estimate, na.rm = TRUE))`
min `r ( min(king_income$estimate, na.rm = TRUE))`
max `r ( max(king_income$estimate, na.rm = TRUE))`
q25 `r ( quantile(king_income$estimate, 0.25, na.rm = TRUE))`
q75 `r ( quantile(king_income$estimate, 0.75, na.rm = TRUE))`

I'm interested in King County household income data because it shows income equility and household affordability, and through exploratory analysis, I found significant income inequality with a right-skewed distribution—where the mean income is notably higher than the median.
